Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-07-08 writeup/rocha_etal.tex
Fixes some figure referencing

The April vorticity-strain jPDF has a shape characteristic of submesoscale turbulence
 (see figures \ref{fig3}a-c). The alignment of vorticity and strain $\alpha \sim \pm\zeta$
 with strong positive skewness are fingerprints of submesoscale fronts
 \citep{shcherbina_etal2013,mcwilliams2016}. The shape of the vorticity-strain
 jPDF is similar for hourly, daily-averaged, and residual velocities, although
 the vorticity skewness reduces from 1.4 to 1.13 from hourly to daily-averaged.
 The April results are characteristic of winter, indicating that wintertime submesoscale
 surface velocity is strongly dominated by submesoscale turbulence --- this is true even for
 superinertial submesoscale currents. The hourly velocity fields are significantly
ageostrophic as depicted by the jPDF of vorticity-Laplacian of SSH
winter \ref{fig3}g). Even in April, only the daily-averaged fields
are largely
in  geostrophic balance (the jPDF of daily-averaged vorticity vs. Laplacian of SSH
is an ellipse with large eccentricity and main axis tilted by 45$^\circ$; figure \ref{fig3}h).

%While there is certainly much to be
%learned using quasi-geostrophic models to study submesoscale turbulence, claims that
%the submesoscale turbulence is dominantly in geostrophic balance
%are overstated \citep{sasaki_etal2014,callies_etal2016};

The October vorticity-strain jPDF shows much weaker skewness (the vorticity skewness
is 0.68 and 0.67 for hourly and daily-averaged velocities). The shape of the
vorticity-strain jPDF  appears to be a combination of two half-ellipses centered
about $\zeta=0$, one with a 45$^\circ$ slope (characteristic of submesocale fronts
that persist in summer) and one with a very steep slope.
That the submesoscale dynamics in October are mainly unbalanced is clearly depicted
in the shape of jPDF of vorticity-Laplacian of SSH for hourly and
residual fields
winter \ref{fig3}j and \ref{fig3}k), which is an ellipse aligned in the vertical axis.
Of course daily-averaging the model suppresses the ageostrophic flows, and
the daily-averaged flow is essentially geostrophic as depicted by the 45$^\circ$-tilted
ellipse in the vorticity-Laplacian of SSH jPDF.

>>>>

The April vorticity-strain jPDF has a shape characteristic of submesoscale turbulence
 (Figures \ref{fig3}a-b). The alignment of vorticity and strain $\alpha \sim \pm\zeta$
 with strong positive skewness are fingerprints of submesoscale fronts
 \citep{shcherbina_etal2013,mcwilliams2016}. The shape of the vorticity-strain
 jPDF is similar for hourly, daily-averaged, although
 the vorticity skewness reduces from 1.4 to 1.13 from hourly to daily-averaged.
 The April results are characteristic of winter, indicating that wintertime submesoscale
 surface velocity is strongly dominated by submesoscale turbulence --- this is true even for
 superinertial submesoscale currents. The hourly velocity fields are significantly
ageostrophic as depicted by the jPDF of vorticity-Laplacian of SSH
winter (Figure \ref{fig3}e). Even in April, only the daily-averaged fields
are largely
in  geostrophic balance (the jPDF of daily-averaged vorticity vs. Laplacian of SSH
is an ellipse with large eccentricity and main axis tilted by 45$^\circ$; Figure \ref{fig3}f).

The October vorticity-strain jPDF shows much weaker skewness (the vorticity skewness
is 0.68 and 0.67 for hourly and daily-averaged velocities). The shape of the
vorticity-strain jPDF  appears to be a combination of two half-ellipses centered
about $\zeta=0$, one with a 45$^\circ$ slope (characteristic of submesocale fronts
that persist in summer) and one with a very steep slope.
That the submesoscale dynamics in October are mainly unbalanced is clearly depicted
in the shape of jPDF of vorticity-Laplacian of SSH for hourly fields
winter (Figure \ref{fig3}g), which is an ellipse aligned in the vertical axis.
Of course daily-averaging the model suppresses the ageostrophic flows, and
the daily-averaged flow is essentially geostrophic as depicted by the 45$^\circ$-tilted
ellipse in the vorticity-Laplacian of SSH jPDF.
